\subsection{Defining a Coherent Value System}
\label{sec:-value}
Subsequent to identifying stakeholders and classifying the stakeholders 
into the basic classes, or new ones depending on the circumstances, we 
must elucidate upon a value system that would act as a guide and in the 
process allow us to reach a conclusion regarding the ethical 
implementation of the automation in question.

We propose a negative utilitarian framework focused on preventing harm, 
where we define harm in terms of violation of a number of values that we 
consider to be important.  We apply this framework with the caveat that 
its usefulness may break down at certain moral extrema, which result in 
a reluctance to make trade-offs between particular harms in particular 
consequences. We identify a rough taxonomy of harms as violations of 
the following values for stakeholders in an ethical analysis:
\begin{enumerate}
  \item Autonomy of Self
    \begin{pointenv}
      Autonomy of self, refers to the basic human rights as laid down 
      by the Universal Declaration Human Rights\cite{assembly1948universal}, 
      which includes but is not limited to, Right to life, Right to freedom 
      of expression

      As laid-down in the Charter, any harm to these basic rights can 
      considered a violation of our framework, and the person responsible for 
      the analysis should eschew any automation that endangers these basic 
      rights, or in the worst case to mitigate these violations through 
      implementation of other practices that would ensure protection of 
      these rights to the highest degree possible.

      A vital point within this tenet is the Right to Privacy, 
      although most people believe this is a fundamental right, in a majority 
      of  cases this would take precedence over any technology that infringes 
      on this right. As we are seeing the battle rage between Apple and the 
      FBI, the protection of this entire section of rights would come under 
      the social contract between the individual/s and society at large. 
    \end{pointenv}

  \item Welfare/Well-Being
    \begin{pointenv}
      The ability to ensure Welfare and well being of self, family and 
      society at large has long been considered the highest 
      responsibility. The world we live in today, this is directly 
      associated with sustenance as well as health.

      Any violation of the welfare of the stakeholders through either 
      contamination of sources of sustenance or loss of livelihood could 
      be considered a violation of this principle. Understandably, there 
      are costs to progress, although this framework aims to minimize 
      the infringements, we propose that on finding a violation, action 
      should be taken against the party to ensure that the cost of 
      implementing the automation would be higher than the gain from such 
      technologies, which are implemented by violating these rules.

      The purpose of this framework is less to take a moral stand but 
      rather a way to balance the effect of consequences on the 
      stakeholders, by suggesting action we believe that the framework 
      used in conjunction with the ground reality would help the user 
      come to an understanding of how to ensure a balance is reached. 
    \end{pointenv}

  \item Economic Concerns
    \begin{pointenv}
      \large outline

      The rights advanced above may sometimes be considered abstract

      talk about how economic means may be leveraged in indirect 
      means

      discuss econmics as a commo framework

      consider that economic issues generally underly all of the above
    \end{pointenv}
\end{enumerate}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
